Simulation Tools for Small Area Estimation: Introducing the \proglang{R}-package \proglang{saeSim}

### 2015-02-20 saeSim.tex
update

%% additional packages and settings which are not part of the template:
\usepackage{wrapfig}
\usepackage{graphicx}
\usepackage{subcaption}

@@

To add the area-level predictions from a Fay-Herriot model we need to define another component. The function takes a \proglang{data.frame} as input and returns the modified version. For the estimation of the EBLUP under the FH model we use the function \proglang{eblupFH} from the package \proglang{sae} \citep{molina13}. To avoid naming conflicts between the dependencies of \proglang{sae} and the package \proglang{dplyr} \citep{wickham14a} we make use of the double colon operator in order to access the function without attaching the package. Hence we define a function named \proglang{comp\_FH} and add it to the process:

@@

\begin{Schunk}
\begin{Sinput}
> ggDat <- reshape2::melt(simResults,
+               id.vars = c("region", "trueStat"), 
+               measure.vars = c("BHF", "direct"), 
+               variable.name = "method",
+               value.name = "prediction")
\end{Sinput}
\end{Schunk}

@@

\section{Outlook}
\label{sec:outlook}
From our perspective, there is a need for sharing tools for data generation and simulation among the scientific community in order to guarantee the reproducibility of research. \proglang{saeSim} may provide an adequate framework for pursuing this aim in the field of small area estimation. By defining the steps of a simulation we may promote a reasonable way to communicate results in academic articles and during research.

>>>>

%% additional packages and settings which are not part of the template:
\usepackage{wrapfig}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{placeins} % \FloatBarrier before conclusion

@@

To add the area-level predictions from a Fay-Herriot model we need to define another component. The function takes a \proglang{data.frame} as input and returns the modified version. For the estimation of the EBLUP under the FH model we use the function \proglang{eblupFH} from the package \proglang{sae} \citep{molina13}. To avoid naming conflicts between the dependencies of \proglang{sae} and the package \proglang{dplyr} \citep{wickham14a} we make use of the double colon operator in order to call the function \proglang{eblupFH} without attaching the package. Hence we define a function named \proglang{comp\_FH} and add it to the process:

@@

\begin{Schunk}
\begin{Sinput}
> ggDat <- reshape2::melt(
+   simResults,
+   id.vars = c("region", "trueStat"), 
+   measure.vars = c("BHF", "direct"), 
+   variable.name = "method",
+   value.name = "prediction")
\end{Sinput}
\end{Schunk}

@@

\FloatBarrier
\section{Outlook}
\label{sec:outlook}
From our perspective, there is a need for sharing tools for data generation and simulation among the scientific community in order to guarantee the reproducibility of research. \proglang{saeSim} may provide an adequate framework for pursuing this aim in the field of small area estimation. By defining the steps of a simulation we may promote a reasonable way to communicate results in academic articles and during research.
